---
title: "assignment4"
author: "Claire Madden"
date: "5/12/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(deSolve)
```




```{r}
source("../R/dynamic_model.R")

# set parameters
C <- 10
years <- seq(from=1, to=300, by=1)
canopy <- 100
carry <- 500
r <- 0.01
g <- 2
temp <- 20


parms = c(canopy = canopy, carry = carry, r = r, g = g, temp = temp, C = C)


c_growth = ode(y=C, times = years, func=forestgrowth, parms=parms)




```

Consider the following model of forest growth (where forest size in measured in units of carbon (C))

dC/dt = 0 when air temperatures are below 0

dC/dt  = r*C for forests where carbon is below a canopy closure threshold 

dC/dt = g. for forests where carbon is above the threshold canopy closure

dC/dt = 0 once carrying capacity is reached.

```{r}

source("../R/model2.R")


# set parameters
initalC <- 10
years <- seq(from=1, to=300, by=1)
canopy <- 100
carry <- 500
r <- 0.01
g <- 2
temp <- 20


parms = c(canopy = canopy, carry = carry, r = r, g = g, temp = temp, initialC = initialC)


c_growth = ode(y=C, times = years, func=forestgrowth, parms=parms)


```


The size of the forest (C), Canopy closure threshold and carrying capacity are all in units of carbon 

You could think of the canopy closure threshold as the size of the forest at which growth rates change from exponential to linear

You can think of r, as early exponential growth rate and g and the linear growth rate 


1. Implement this model in R (as a differential equation)

2. Run the model for 300 years (using the ODE solver)  starting with an initial forest size of 10 kg/C, and using the following parameters

canopy closure threshold of 100 kgC  - canopy

a carrying capacity of 500 kg C - carry

a early growth rate of 0.01 - r

 a later growth rate of 2 kg/year - g

an air temperature of 20C - temp

Graph the results

3. Run a sobol sensitivity analysis that explores how the estimated maximum forest size varies with early and later growth rates. 

Graph the results of the sensitivity analysis as a box plot and a plot of the two sobol indices (S and T)



Submit R markdown with model implementation, graphs and sensitivity analysis and R file with your model



